The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
less but still weak

<!-- TODO: weak -->
Multilayer networks can be used to explicitly consider habitat selection and
sociality across scales. Animal social systems can be parsed by spatial
contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
The effect of seasonality of resources can can be directly measured by differences in
habitat selection and sociality across temporal layers. Habitat selection can be
explicitly integrated using network layers defined by similarity of selection
coefficients between individuals. These explicit integration of habitat
selection and sociality across social, spatial and temporal scales highlight the
potential for novel insights from multilayer networks.

>>>>

<!-- TODO: weak --> 
Multilayer networks can be used to explicitly consider
habitat selection and sociality across scales. Animal social systems can be
parsed by spatial contexts, defined, for example, by habitat types as in Figure
\@ref(fig:lcres). The effect of seasonality of resources can can be directly
measured by differences in habitat selection and sociality across temporal
layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
selection can be explicitly integrated using network layers defined by selection
coefficients for individuals. These examples of explicit integrations of habitat selection
and sociality across social, spatial and temporal scales highlight the potential
for novel insights from multilayer networks.
